---
title: "notebook"
author: "Juliette Verstaen"
date: "11/8/2019"
output: html_document
---

THIS CODE BELOW IS ALL JAVA SCRIPT STUFF probably wont need it but you never know

Here is the code to save it as a .json file if we ever need it 
data_json <- d3_nest(data)

# Save in a json file
write(data_json, "data_ready.json")


##Create dendogram!
Note: We are now writting in Java Script, so the code chunks are "js" instead of "r" 
Code is from [this](https://www.d3-graph-gallery.com/graph/dendrogram_radial_basic.html) tutorial website 
```{js}
<!DOCTYPE html>
<meta charset="utf-8">

<!-- Load d3.js -->
<script src="https://d3js.org/d3.v4.js"></script>

<!-- Create a div where the graph will take place -->
<div id="my_dataviz"></div>
```

```{js}

<script>

// set the dimensions and margins of the graph
var width = 460
var height = 460
var radius = width / 2 // radius of the dendrogram

// append the svg object to the body of the page
var svg = d3.select("#my_dataviz")
  .append("svg")
    .attr("width", width)
    .attr("height", height)
  .append("g")
    .attr("transform", "translate(" + radius + "," + radius + ")");

// read json data
d3.json("data_ready.json", function(data) {

  // Create the cluster layout:
  var cluster = d3.cluster()
    .size([360, radius - 60]);  // 360 means whole circle. radius - 60 means 60 px of margin around dendrogram

  // Give the data to this cluster layout:
  var root = d3.hierarchy(data, function(d) {
      return d.children;
  });
  cluster(root);

  // Features of the links between nodes:
  var linksGenerator = d3.linkRadial()
      .angle(function(d) { return d.x / 180 * Math.PI; })
      .radius(function(d) { return d.y; });

  // Add the links between nodes:
  svg.selectAll('path')
    .data(root.links())
    .enter()
    .append('path')
      .attr("d", linksGenerator)
      .style("fill", 'none')
      .attr("stroke", '#ccc')


  // Add a circle for each node.
  svg.selectAll("g")
      .data(root.descendants())
      .enter()
      .append("g")
      .attr("transform", function(d) {
          return "rotate(" + (d.x - 90) + ")translate(" + d.y + ")";
      })
      .append("circle")
        .attr("r", 7)
        .style("fill", "#69b3a2")
        .attr("stroke", "black")
        .style("stroke-width", 2)

})

</script>

```


Alright, I'm getting a little stuck here because I'm starting from scratch with my Java language skills! Am I creating a graph? where is it saving to? What's "div" ?? So I can either spend a lot of time learning Java and Html/CSS (which I may want to anyways), or go down this path of another package I found called r2d3. We'll start with that

## Learning and Exploring r2d3 package

This package is already more my jam. I need the hex sticker, it's so cite!
Using [this](https://blog.rstudio.com/2018/10/05/r2d3-r-interface-to-d3-visualizations/) tutorial

```{r}
#install.packages("r2d3")
library(r2d3)

data_json
```



```{r}
r2d3(script = rad_dend.js)
```

Ok now try this 
https://observablehq.com/@d3/radial-dendrogram

```{d3}
chart = {
  const root = tree(d3.hierarchy(data)
      .sort((a, b) => (a.height - b.height) || a.data.name.localeCompare(b.data.name)));

  const svg = d3.create("svg")
      .style("max-width", "100%")
      .style("height", "auto")
      .style("font", "10px sans-serif")
      .style("margin", "5px");
  
  const link = svg.append("g")
      .attr("fill", "none")
      .attr("stroke", "#555")
      .attr("stroke-opacity", 0.4)
      .attr("stroke-width", 1.5)
    .selectAll("path")
    .data(root.links())
    .enter().append("path")
      .attr("d", d3.linkRadial()
          .angle(d => d.x)
          .radius(d => d.y));
  
  const node = svg.append("g")
      .attr("stroke-linejoin", "round")
      .attr("stroke-width", 3)
    .selectAll("g")
    .data(root.descendants().reverse())
    .enter().append("g")
      .attr("transform", d => `
        rotate(${d.x * 180 / Math.PI - 90})
        translate(${d.y},0)
      `);
  
  node.append("circle")
      .attr("fill", d => d.children ? "#555" : "#999")
      .attr("r", 2.5);
  
  node.append("text")
      .attr("dy", "0.31em")
      .attr("x", d => d.x < Math.PI === !d.children ? 6 : -6)
      .attr("text-anchor", d => d.x < Math.PI === !d.children ? "start" : "end")
      .attr("transform", d => d.x >= Math.PI ? "rotate(180)" : null)
      .text(d => d.data.name)
    .filter(d => d.children)
    .clone(true).lower()
      .attr("stroke", "white");

  yield svg.node();

  svg.attr("viewBox", autoBox);
}

#############

function autoBox() {
  const {x, y, width, height} = this.getBBox();
  return [x, y, width, height];
}

data = FileAttachment("data_ready.json").json()

width = 975

radius = width / 2

tree = d3.cluster().size([2 * Math.PI, radius - 100])

d3 = require("d3@5")
```


```{js, barchart}
// !preview r2d3 data=c(0.3, 0.6, 0.8, 0.95, 0.40, 0.20)

var barHeight = Math.floor(height / data.length);

svg.selectAll('rect')
  .data(data)
  .enter().append('rect')
    .attr('width', function(d) { return d * width; })
    .attr('height', barHeight)
    .attr('y', function(d, i) { return i * barHeight; })
    .attr('fill', 'steelblue');
```


```{r}
library(r2d3)
r2d3(data=c(0.3, 0.6, 0.8, 0.95, 0.40, 0.20), script = "barchart.js")
```


## OKAY lets maybe leave the whole java script thing for a bit. I found some simplier fully based in R code for dendograms. They are ugly, but maybe it's a good starting point and I can work on making them prettier
https://www.r-graph-gallery.com/340-custom-your-dendrogram-with-dendextend.html

```{r}
# Library
library(tidyverse)
library(ape)
 
# Data
head(mtcars)
 
# Clusterisation using 3 variables
mtcars %>% 
  select(mpg, cyl, disp) %>% 
  dist() %>% 
  hclust()
#%>%  as.dendrogram() -> dend
 
# Plot
par(mar=c(7,3,1,1))  # Increase bottom margin to have the complete label
plot(mtcars, type = "radial")
```















